Software Ticket Quality

### 2017-11-26 proposal/mprop.tex
Combine first two papers in data quality

2nd and 3rd papers both investigate what quality means.

Several authors have investigated the \emph{meaning} of quality.   \cite{sucansuch2018} said ..

@@

\citet{bachmann2009software} attempted to compute quality metrics for a range of project data sources, including bug tracking databases, version control logs.  They attempted to link bug tracking and change logs and showed that the closed source project investigated reported higher quality metrics.

\citet{}

\textbf{Software Process Data Quality and Characteristics}\cite{bachmann2009software}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors are trying to investigate different software process data
    (e.g. bug tracking databases, version control systems logs) in order to
    infer quality and characteristics. Then, they want to compute measures
    and discuss the issues that arise from these observations.
  \item \textbf{What was the method?}
    They examined 6 software projects, 5 of which were open source, by extracting
    the SVN and CVS logs, as well as the content of the bug tracker databases. Then,
    they tried to link the logs with the contents of the bug tracker databases as they
    are not integrated by default. 
  \item \textbf{What did they learn?}
    Firstly, the closed source project the authors examined showed much more data
    quality as the open source counterparts, among which better average attachments 
    per bug report, better average status changes per bug report or average commits
    per bug report/developer. Moreover, the authors found that there is little linkage
    between bug reports and version control logs, thus reducing the overall traceability.
    Also, there is reduced quality in change logs as, for example, the Eclipse project
    has more than 20\% empty commit messages. In conclusion, closed source projects will
    probably exhibit improved data quality than open source ones, but data quality in general
    differs from project to project.
  \item \textbf{Relevance to our work}:
    The analysis on data quality in open/closed source projects presented in this 
    research is valuable to us as it presents various statistics on commits, bug report
    structure and quality, as well as linkage between the two. We might apply the techniques
    in our own research on ticket quality.
\end{itemize}

@@

\textbf{Organizational Impact of 
        Information Quality}\cite{gorla2010organizational}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors had two main research questions they wanted to address:
      \begin{itemize}
        \item what individual/combined influences system quality, service quality,
          information quality have on organizational impact?
        \item what effect does system quality have on information quality?
      \end{itemize}
  \item \textbf{What was the method?}
    They conducted a construct measurement for the IS quality dimensions and 
    collected data through empirical testing.
  \item \textbf{What did they learn?}
    Firstly, they learned that service quality has the greatest impact 
    of all three quality constructs. Moreover, they found out that there is a 
    linkage between system and information quality, fact that previous research
    did not reveal. Lastly, their results indicate that the above-mentioned 
    quality dimensions have a significant positive influence on organizational
    impact either directly or indirectly.
  \item \textbf{Relevance to our work}: the paper can provide us insights into
    how valuable information quality is and what an impact it can have.
\end{itemize}

>>>>

Several authors have investigated the \emph{meaning} of data quality, how to 
\emph{measure} it and what \emph{impact} poor data quality has on software 
projects.

\citet{bachmann2009software} conducted a thorough investigation of several
software projects, both open source (5 projects) as well as closed source (1 
project), in order to infer what determines if it has quality. They selected 
various sources of information, among which bug tracking 
databases and version control systems logs, and examined SVN logs, CVS logs
and the content of the bug tracker databases, in the end trying to link 
the logs with the bug tracker contents as they are not integrated by default. 
On the other hand, \citet{strong1997data} conducted a qualitative analysis
instead of quantitative by collecting data from 42 data quality projects by 
interviewing custodians, customers and managers. They analyzed each project
using the data quality dimensions as content analysis codes.

The first study came to several conclusions, among which:
  \begin{itemize}
    \item closed source software projects usually exhibit better data quality 
    (i.e. better average number of attachments, better average status changes, 
    better average number of commits per bug report);
    \item reduced traceability between bug reports and version control logs
    due to scarce linkage between the two;
    \item open source projects exhibit reduced quality in change logs as,
    for example, the Eclipse project has over 20\% empty commit messages.
  \end{itemize}
However, the second study reached the conclusion that representational data 
quality dimensions are underlying causes of accessibility data quality problem
patterns. The authors also found out that three underlying causes for users'
complaints regarding data not supporting their tasks are incomplete data, 
inadequately defined or measured data and data that could not be appropriately
aggregated.

@@

@@

\textbf{Organizational Impact of Information Quality}
\cite{gorla2010organizational}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors had two main research questions they wanted to address:
      \begin{itemize}
        \item what individual/combined influences system quality, service quality,
          information quality have on organizational impact?
        \item what effect does system quality have on information quality?
      \end{itemize}
  \item \textbf{What was the method?}
    They conducted a construct measurement for the IS quality dimensions and 
    collected data through empirical testing.
  \item \textbf{What did they learn?}
    Firstly, they learned that service quality has the greatest impact 
    of all three quality constructs. Moreover, they found out that there is a 
    linkage between system and information quality, fact that previous research
    did not reveal. Lastly, their results indicate that the above-mentioned 
    quality dimensions have a significant positive influence on organizational
    impact either directly or indirectly.
  \item \textbf{Relevance to our work}: the paper can provide us insights into
    how valuable information quality is and what an impact it can have.
\end{itemize}
